Predictive Regressions with Persistent Regressors

### 2019-09-10 paper.tex
ADD intro

\begin{abstract}
Campbell and Yogo (2006) propose a Bonferroni-type procedure for valid inference of predictive regressions with almost non-stationary regressors. In this study, I will explain the rationale behind their method, replicate empirical findings, and extend them with out-of-sample data that surfaced since their method's publication. Further, I will investigate via Monte Carlo simulation the method's behavior when its assumptions are violated in ways likely encountered in practice. 
\end{abstract}

\section{Introduction}
The question whether asset returns can be predicted with the help of observable variables is of great interest to financial institutions and the public as a whole. One of the most intuitive relationships exists between the price of a company's stock and the discounted earnings it will generate in the future. Since future earnings are not observable, current earnings or dividends or moving averages of them are often used as a proxy. To statistically test whether these variables can indeed predict future stock returns one may fit a linear model of the form 
\begin{align} 
r_{t} = \alpha + \beta x_{t-1} + u_{t} \\ 
x_{t} = \gamma + \rho  x_{t-1} + e_{t}
\end{align}
and perform a t-test on the $\beta$ coefficient.

\paragraph{Outline}

\section{The regression setup and its problem
}
With log-returns $r_{t}$ observable at time $t$ and lagged supposedly predictive variable $x_{t-1}$ observable at $t-1$  Campbell and Yogo (2006) consider the regression system
\begin{align} 
\label{eqn:1}
r_{t} = \alpha + \beta x_{t-1} + u_{t} \\ 
\label{eqn:2}
x_{t} = \gamma + \rho  x_{t-1} + e_{t}
\end{align}
They further assume normality i.e. $w_{t}=\left(u_{t}, e_{t}\right)^{\prime} \stackrel{i i d}{\sim} \mathrm{N}(\boldsymbol{0}, \boldsymbol{\Sigma})$ where  $\boldsymbol{\Sigma}=\left[\begin{array}{cc}{\sigma_{u}^{2}} & {\sigma_{u e}} \\ {\sigma_{u e}} & {\sigma_{e}^{2}}\end{array}\right]$ is known .

@@

\section{Derivation of the tests}
\subsection{Infeasible tests}
In developing their test, Campbell and Yogo (2006) start by considering the t-statistic 
\begin{equation}
t\left(\beta_{0}\right)=\frac{\widehat{\beta}-\beta_{0}}{\sigma_{u}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{-1 / 2}}
\end{equation}
where $x_{t-1}^{\mu}=x_{t-1}-T^{-1} \sum_{t=1}^{T} x_{t-1}$ denotes the de-meaned regressor and $\widehat{\beta}$ is the OLS estimate of $\beta$. They argue that this test ignores information contained in the system (2) and can thus not be optimal. To see this consider the joint log likelihood function of the system ($\ref{eqn:1}$, $\ref{eqn:2}$)
\begin{equation}
\begin{aligned} L(\beta, \rho, \alpha, \gamma)=&-\frac{1}{1-\delta^{2}} \sum_{t=1}^{T}\left[\frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}}{\sigma_{u}^{2}}-2 \delta \frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)\left(x_{t}-\gamma-\rho x_{t-1}\right)}{\sigma_{u} \sigma_{e}}\right.\\ &\left.+\frac{\left(x_{t}-\gamma-\rho x_{t-1}\right)^{2}}{\sigma_{e}^{2}}\right] \end{aligned}
\end{equation}
and observe that the t-test squared is equal to the likelihood ratio test statistic
\begin{equation}
\max _{\beta, \rho, \alpha, \gamma} L(\beta, \rho, \alpha, \gamma)-\max _{\rho, \alpha, \gamma} L\left(\beta_{0}, \rho, \alpha, \gamma\right)=t\left(\beta_{0}\right)^{2}
\end{equation}
But this test statistic turns out to be the same if only the marginal log likelihood 
\begin{equation}
L(\beta, \alpha)=-\sum_{t=1}^{T}\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}
\end{equation}
is used in its computation. Thus the t-test ignores information about $\rho$.

@@

\subsection{Making the Q-test feasible}
When the pretest cannot reject the null of unacceptable size distortion we cannot use the unadjusted t-test to do inference. While the Q-test is UMP when $\rho$ and $\delta$ are known, in practice this is not the case. Furthermore, $\rho$ cannot be estimated consistently since $\operatorname{Var}\left(x_{t}\right)=\frac{\sigma_{e}^{2}}{1-\rho^{2}}$ gets large if $\rho$ is local to unity. Instead, as described in the previous section, Campbell and Yogo (2006) construct a $100\left(1-\alpha_{1}\right) \%$ confidence interval, $C_{\rho}\left(\alpha_{1}\right)$ for $\rho$ from a unit root test statistic. They then construct $C_{\beta | \rho}\left(\alpha_{2}\right)$, a $100\left(1-\alpha_{2}\right) \%$ conditional on $\rho$ confidence interval for $\beta$. To marginalize $\rho$ and thus getting an unconditional confidence interval for $\beta$ they take the union over $\rho \in C_{\rho}\left(\alpha_{1}\right)$
\begin{equation}
C_{\beta}(\alpha)=\bigcup_{\rho \in C_{\rho}\left(\alpha_{1}\right)} C_{\beta | \rho}\left(\alpha_{2}\right)
\end{equation}

@@

\section{Monte Carlo simulation}

To confirm the correct implementation of the procedure, Table~\vref{tab:cy} replicates Table 3 of Campbell and Yogo (2006) with the same input parameters. For each parameter combination 10,000 Monte Carlo samples are drawn from a multivariate standard normal distribution with correlation $\delta$. These variates represent the innovations, which are used to simulate sample paths according to system ($\ref{eqn:1}$, $\ref{eqn:2}$). The null hypothesis $H_0: \beta = 0$ is tested against the alternative $H_1: \beta > 0$ at the 5\% significance level. If the Bonferroni confidence interval lies strictly above zero, the one-sided test is rejected. 
\begin{table}[hb!]
\caption{Finite-sample rejection rates}
\label{tab:cy}
\centering

@@

Next, slightly different input parameters are chosen. If the results differ qualitatively, the previous findings might be the result of selection bias. As demonstrated by Table~\vref{tab:cy_changed}, no such suspicion is warranted. As long as the sample size is at least 100 and $\rho$ is local to unity, the Bonferroni Q-test has acceptable finite sample rejection rates. The infeasible Q-test, unsurprisingly, always has rejection rates close to $\alpha$. The t-test, on the other hand, significantly over-rejects when the innovations are highly correlated and $\rho$ is local to unity. It should be noted, however, that the two-sided Bonferroni Q-test tends to under-reject for the chosen parameters. 
\begin{table}[h!]
\caption{Finite-sample rejection rates}
\centering
\label{tab:cy_changed}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrr}
  \hline
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test & Bonf. Q-test (two-sided) \\ 
  \hline
1 & 50 & 0 & 1.000 & -0.99 & 0.4442 & 0.0863 & 0.0544 & 0.0864 \\ 
  2 & 50 & 0 & 1.000 & -0.90 & 0.3786 & 0.0943 & 0.0506 & 0.0953 \\ 
  3 & 50 & -1 & 0.980 & -0.99 & 0.3502 & 0.0857 & 0.0486 & 0.0898 \\ 
  4 & 50 & -1 & 0.980 & -0.90 & 0.3107 & 0.0949 & 0.0489 & 0.0964 \\ 
  5 & 50 & -10 & 0.804 & -0.99 & 0.1440 & 0.0821 & 0.0512 & 0.1004 \\ 
  6 & 50 & -10 & 0.804 & -0.90 & 0.1226 & 0.0840 & 0.0472 & 0.0929 \\ 
  7 & 50 & -15 & 0.706 & -0.99 & 0.1114 & 0.0895 & 0.0485 & 0.1112 \\ 
  8 & 50 & -15 & 0.706 & -0.90 & 0.1035 & 0.0981 & 0.0468 & 0.1112 \\ 
  9 & 150 & 0 & 1.000 & -0.99 & 0.4467 & 0.0508 & 0.0508 & 0.0509 \\ 
  10 & 150 & 0 & 1.000 & -0.90 & 0.3804 & 0.0524 & 0.0494 & 0.0554 \\ 
  11 & 150 & -1 & 0.993 & -0.99 & 0.3584 & 0.0475 & 0.0493 & 0.0611 \\ 
  12 & 150 & -1 & 0.993 & -0.90 & 0.3137 & 0.0572 & 0.0532 & 0.0625 \\ 
  13 & 150 & -10 & 0.934 & -0.99 & 0.1510 & 0.0468 & 0.0480 & 0.0720 \\ 
  14 & 150 & -10 & 0.934 & -0.90 & 0.1309 & 0.0534 & 0.0484 & 0.0672 \\ 
  15 & 150 & -15 & 0.901 & -0.99 & 0.1273 & 0.0446 & 0.0520 & 0.0819 \\ 
  16 & 150 & -15 & 0.901 & -0.90 & 0.1133 & 0.0484 & 0.0489 & 0.0695 \\ 
  17 & 200 & 0 & 1.000 & -0.99 & 0.4477 & 0.0435 & 0.0478 & 0.0438 \\ 
  18 & 200 & 0 & 1.000 & -0.90 & 0.3786 & 0.0501 & 0.0520 & 0.0546 \\ 
  19 & 200 & -1 & 0.995 & -0.99 & 0.3582 & 0.0449 & 0.0483 & 0.0607 \\ 
  20 & 200 & -1 & 0.995 & -0.90 & 0.3127 & 0.0542 & 0.0468 & 0.0615 \\ 
  21 & 200 & -10 & 0.950 & -0.99 & 0.1490 & 0.0401 & 0.0497 & 0.0666 \\ 
  22 & 200 & -10 & 0.950 & -0.90 & 0.1352 & 0.0486 & 0.0502 & 0.0634 \\ 
  23 & 200 & -15 & 0.925 & -0.99 & 0.1276 & 0.0369 & 0.0487 & 0.0786 \\ 
  24 & 200 & -15 & 0.925 & -0.90 & 0.1234 & 0.0482 & 0.0491 & 0.0670 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed and two-tailed Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

As argued by Phillips (2014), the Q-test as derived in section (3) is asymptotically invalid when the largest autoregressive root of the regressor is not local to unity. In the following I will demonstrate the finite sample behavior as $\rho$ diverges from unity. Again 10,000 Monte Carlo simulations are run with Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of Campbell and Yogo (2005). Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood the Bonferroni Q-test significantly over-rejects the true null of no predictability. 
\begin{table}[h!]
\caption{Finite-sample rejection rates (non local to unity autoregressive root) }
\label{tab:non-local}
\centering
\begin{threeparttable}
\begin{tabular}{rrrrrrrrr}
  \hline
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test & Bonf. Q-test (two-sided) \\ 
  \hline
1 & 50 & 0 & 1.000 & -0.95 & 0.4147 & 0.0946 & 0.0480 & 0.0957 \\ 
  2 & 50 & 0 & 1.000 & -0.75 & 0.2810 & 0.0838 & 0.0475 & 0.0870 \\ 
  3 & 50 & 0 & 1.000 & -0.50 & 0.1758 & 0.0846 & 0.0536 & 0.0940 \\ 
  4 & 50 & -5 & 0.902 & -0.95 & 0.1887 & 0.0896 & 0.0499 & 0.0980 \\ 
  5 & 50 & -5 & 0.902 & -0.75 & 0.1487 & 0.0830 & 0.0522 & 0.0891 \\ 
  6 & 50 & -5 & 0.902 & -0.50 & 0.1081 & 0.0701 & 0.0512 & 0.0811 \\ 
  7 & 50 & -10 & 0.804 & -0.95 & 0.1325 & 0.0894 & 0.0543 & 0.1018 \\ 
  8 & 50 & -10 & 0.804 & -0.75 & 0.1126 & 0.0789 & 0.0462 & 0.0867 \\ 
  9 & 50 & -10 & 0.804 & -0.50 & 0.0887 & 0.0689 & 0.0510 & 0.0820 \\ 
  10 & 50 & -20 & 0.608 & -0.95 & 0.0987 & 0.1266 & 0.0506 & 0.1469 \\ 
  11 & 50 & -20 & 0.608 & -0.75 & 0.0906 & 0.1087 & 0.0506 & 0.1216 \\ 
  12 & 50 & -20 & 0.608 & -0.50 & 0.0682 & 0.0800 & 0.0443 & 0.0948 \\ 
  13 & 50 & -30 & 0.412 & -0.95 & 0.0811 & 0.1666 & 0.0455 & 0.1961 \\ 
  14 & 50 & -30 & 0.412 & -0.75 & 0.0787 & 0.1272 & 0.0500 & 0.1460 \\ 
  15 & 50 & -30 & 0.412 & -0.50 & 0.0719 & 0.1003 & 0.0523 & 0.1195 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed and two-tailed Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with non local to unity autoregressive root. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

In the CCC-GARCH model it has been assumed that there are no volatility transmissions between the returns and the regressor. This assumption seems unrealistic and it reduces the correlation between the residuals as demonstrated by $\hat{\delta}$. There are various multivariate GARCH models suited for incorporating spill-over effects such as the BEKK model of Engle and Kroner (1995). It seems plausible, though, that the variances of both the regressor and the returns share a common stochastic trend which may be imagined as the overall economic uncertainty. This seems reasonable since it is hard to imagine having high variance in returns without having high variance in valuation ratios and vice versa. Parameter estimates of the univariate GARCH model based on monthly returns from 1926 to 2003 are displayed in Table~\vref{tab:garch_est}. Since $\hat{\alpha}+\hat{\beta}=0.983$ is close to 1, at which point the covariance stationarity condition is violated, concern of conditional heteroskedasticity of real returns leading to invalid inference using the feasible Q-test is justified.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GARCH(1, 1)} 
  \label{tab:garch_est} 
  \begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00002$ & $2.553$ & $0.011$ \\ 
$\alpha$ & $0.107$ & $0.020$ & $5.331$ & $0.000$ \\ 
$\beta$ & $0.876$ & $0.020$ & $44.365$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{abstract}
Campbell and Yogo (2006) propose a Bonferroni-type procedure for valid inference of predictive regressions with almost nonstationary regressors. In this study, I will explain the rationale behind their method, replicate empirical findings, and extend them with out-of-sample data that surfaced since their method's publication. Further, I will investigate via Monte Carlo simulation the method's behavior when its assumptions are violated in ways likely encountered in practice. 
\end{abstract}

\section{Introduction}
The question whether asset returns can be predicted with the help of observable variables is of great interest to financial institutions and the public as a whole. One of the most economically intuitive relationships exists between the price of a company's stock and the discounted earnings it will generate in the future. Since future earnings are not observable, current earnings or dividends or moving averages of them are often used as a proxy. To statistically test whether these variables are indeed predictive, one may test the significance of coefficients in a regression of the supposedly predictive variable onto equity market returns. The most straightforward way of doing this is via the t-test. Elliott and Stock (1994) find that this test has a nonstandard distribution under the null if the largest autoregressive root of the regressor is close to unity and the innovations of regressor and regressand are correlated. Given the presence of these nuisances, the t-test will lead to invalid inference. In this context, Campbell and Yogo (2006) develop a test that exploits information about the autoregressive root of the regressor and thus tries to overcome this issue. Section $\ref{regression}$ formalizes the regression setup and outlines the problem. Section $\ref{Derivation of the tests}$ explains the derivation of the Campbell and Yogo's (2006) test. This is done by first considering optimal tests, albeit under unrealistic assumptions, in section $\ref{Infeasible tests}$. This section also establishes the conditions for a nonstandard distribution of the t-statistic. A pretest based on these conditions is described in section $\ref{pretest}$. Section $\ref{Making the Q-test feasible}$ details the use of Bonferroni's inequality in making the test feasible.  The test is further generalized to more realistic assumptions in section $\ref{implementation}$ and its mathematical implementation is described. Section $\ref{power}$ summarizes the power advantages of the test found by Campbell and Yogo (2006). Section $\ref{Monte Carlo simulation}$ proceeds with evaluating finite-sample rejection rates of the feasible Q-test under various innovation distributions and violations of assumptions made in section $\ref{implementation}$. First, Monte Carlo evidence of Campbell and Yogo (2006) is scrutinized and replicated in section $\ref{Simulation with Gaussian innovations}$. Section $\ref{Simulation with weakly persistent regressors and Gaussian innovations}$ demonstrates over-rejection in finite-samples when the largest autoregressive root of the regressor is nonlocal-to-unity. An attempt of modeling innovations by a multivariate GARCH process is then made in section $\ref{Simulation with CCC-GARCH innovations}$. This is further refined in section $\ref{Simulation with common GARCH innovations}$ where it is hypothesized that innovations variances of both the regressor and the regressand share a common stochastic trend that is modeled by a GARCH process. Section $\ref{Simulation with common GJR-GARCH innovations}$ concludes the Monte Carlo evidence by simulation of the common stochastic trend by GJR-GARCH with conditional leptokurtosis. Empirical findings are replicated and evaluated on out-of-sample data in section $\ref{Empirical Results}$. Finally, section $\ref{conclusion}$ concludes.

\section{The regression setup and its problem}
\label{regression}
With log-returns $r_{t}$ observable at time $t$ and lagged supposedly predictive variable $x_{t-1}$ observable at $t-1$  Campbell and Yogo (2006) consider the regression system
\begin{align} 
\label{eqn:1}
r_{t} = \alpha + \beta x_{t-1} + u_{t} \\ 
\label{eqn:2}
x_{t} = \gamma + \rho  x_{t-1} + e_{t}
\end{align}
They further assume normality i.e. $w_{t}=\left(u_{t}, e_{t}\right)^{\prime} \stackrel{i i d}{\sim} \mathrm{N}(\boldsymbol{0}, \boldsymbol{\Sigma})$ where  $\boldsymbol{\Sigma}=\left[\begin{array}{cc}{\sigma_{u}^{2}} & {\sigma_{u e}} \\ {\sigma_{u e}} & {\sigma_{e}^{2}}\end{array}\right]$ is known .

@@

\section{Derivation of the tests}
\label{Derivation of the tests}
\subsection{Infeasible tests}
\label{Infeasible tests}
In developing their test, Campbell and Yogo (2006) start by considering the t-statistic 
\begin{equation}
t\left(\beta_{0}\right)=\frac{\widehat{\beta}-\beta_{0}}{\sigma_{u}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{-1 / 2}}
\end{equation}
where $x_{t-1}^{\mu}=x_{t-1}-T^{-1} \sum_{t=1}^{T} x_{t-1}$ denotes the de-meaned regressor and $\widehat{\beta}$ is the OLS estimate of $\beta$. They argue that this test ignores information contained in the system (2) and can thus not be optimal. To see this consider the joint log likelihood function of the system ($\ref{eqn:1}$, $\ref{eqn:2}$)
\begin{equation}
\begin{aligned} L(\beta, \rho, \alpha, \gamma)=&-\frac{1}{1-\delta^{2}} \sum_{t=1}^{T}\left[\frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}}{\sigma_{u}^{2}}-2 \delta \frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)\left(x_{t}-\gamma-\rho x_{t-1}\right)}{\sigma_{u} \sigma_{e}}\right.\\ &\left.+\frac{\left(x_{t}-\gamma-\rho x_{t-1}\right)^{2}}{\sigma_{e}^{2}}\right] \end{aligned}
\end{equation}
and observe that the t-test squared is equal to the likelihood ratio test statistic
\begin{equation}
\max _{\beta, \rho, \alpha, \gamma} L(\beta, \rho, \alpha, \gamma)-\max _{\rho, \alpha, \gamma} L\left(\beta_{0}, \rho, \alpha, \gamma\right)=t\left(\beta_{0}\right)^{2}
\end{equation}
But this test statistic turns out to be the same if only the marginal log likelihood 
\begin{equation}
L(\beta, \alpha)=-\sum_{t=1}^{T}\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}
\end{equation}
is used in its computation. Thus the t-test ignores information about $\rho$.

@@

\subsection{Making the Q-test feasible}
\label{Making the Q-test feasible}
When the pretest cannot reject the null of unacceptable size distortion we cannot use the unadjusted t-test to do inference. While the Q-test is UMP when $\rho$ and $\delta$ are known, in practice this is not the case. Furthermore, $\rho$ cannot be estimated consistently since $\operatorname{Var}\left(x_{t}\right)=\frac{\sigma_{e}^{2}}{1-\rho^{2}}$ gets large if $\rho$ is local to unity. Instead, as described in the previous section, Campbell and Yogo (2006) construct a $100\left(1-\alpha_{1}\right) \%$ confidence interval, $C_{\rho}\left(\alpha_{1}\right)$ for $\rho$ from a unit root test statistic. They then construct $C_{\beta | \rho}\left(\alpha_{2}\right)$, a $100\left(1-\alpha_{2}\right) \%$ conditional on $\rho$ confidence interval for $\beta$. To marginalize $\rho$ and thus getting an unconditional confidence interval for $\beta$ they take the union over $\rho \in C_{\rho}\left(\alpha_{1}\right)$
\begin{equation}
C_{\beta}(\alpha)=\bigcup_{\rho \in C_{\rho}\left(\alpha_{1}\right)} C_{\beta | \rho}\left(\alpha_{2}\right)
\end{equation}

@@

\section{Monte Carlo simulation}
\label{Monte Carlo simulation}
\subsection{Simulation with Gaussian innovations}
\label{Simulation with Gaussian innovations}
To confirm the correct implementation of the procedure, Table~\vref{tab:cy} replicates Table 3 of Campbell and Yogo (2006) with the same input parameters. For each parameter combination 10,000 Monte Carlo samples are drawn from a multivariate standard normal distribution with correlation $\delta$. These variates represent the innovations, which are used to simulate sample paths according to system ($\ref{eqn:1}$, $\ref{eqn:2}$). The null hypothesis $H_0: \beta = 0$ is tested against the alternative $H_1: \beta > 0$ at the 5\% significance level. If the Bonferroni confidence interval lies strictly above zero, the one-sided test is rejected. 
\begin{table}[hb!]
\caption{Finite-sample rejection rates}
\label{tab:cy}
\centering

@@

Next, slightly different input parameters are chosen. If the results differ qualitatively, the previous findings might be the result of selection bias. As demonstrated by Table~\vref{tab:cy_changed}, no such suspicion is warranted. As long as the sample size is at least 100 and $\rho$ is local to unity, the Bonferroni Q-test has acceptable finite sample rejection rates. The infeasible Q-test, unsurprisingly, always has rejection rates close to $\alpha$. The t-test, on the other hand, significantly over-rejects when the innovations are highly correlated and $\rho$ is local to unity. It should be noted, however, that the two-sided Bonferroni Q-test tends to under-reject for the chosen parameters. 
\begin{table}[h!]
\caption{Finite-sample rejection rates}
\label{tab:cy_changed}
\begin{tabular}{rrrrrrrrr}
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test & Bonf. Q-test (two-sided) \\ 
1 & 50 & 0 & 1.000 & -0.99 & 0.4442 & 0.0863 & 0.0544 & 0.0864 \\ 
  2 & 50 & 0 & 1.000 & -0.90 & 0.3786 & 0.0943 & 0.0506 & 0.0953 \\ 
  3 & 50 & -1 & 0.980 & -0.99 & 0.3502 & 0.0857 & 0.0486 & 0.0898 \\ 
  4 & 50 & -1 & 0.980 & -0.90 & 0.3107 & 0.0949 & 0.0489 & 0.0964 \\ 
  5 & 50 & -10 & 0.804 & -0.99 & 0.1440 & 0.0821 & 0.0512 & 0.1004 \\ 
  6 & 50 & -10 & 0.804 & -0.90 & 0.1226 & 0.0840 & 0.0472 & 0.0929 \\ 
  7 & 50 & -15 & 0.706 & -0.99 & 0.1114 & 0.0895 & 0.0485 & 0.1112 \\ 
  8 & 50 & -15 & 0.706 & -0.90 & 0.1035 & 0.0981 & 0.0468 & 0.1112 \\ 
  9 & 150 & 0 & 1.000 & -0.99 & 0.4467 & 0.0508 & 0.0508 & 0.0509 \\ 
  10 & 150 & 0 & 1.000 & -0.90 & 0.3804 & 0.0524 & 0.0494 & 0.0554 \\ 
  11 & 150 & -1 & 0.993 & -0.99 & 0.3584 & 0.0475 & 0.0493 & 0.0611 \\ 
  12 & 150 & -1 & 0.993 & -0.90 & 0.3137 & 0.0572 & 0.0532 & 0.0625 \\ 
  13 & 150 & -10 & 0.934 & -0.99 & 0.1510 & 0.0468 & 0.0480 & 0.0720 \\ 
  14 & 150 & -10 & 0.934 & -0.90 & 0.1309 & 0.0534 & 0.0484 & 0.0672 \\ 
  15 & 150 & -15 & 0.901 & -0.99 & 0.1273 & 0.0446 & 0.0520 & 0.0819 \\ 
  16 & 150 & -15 & 0.901 & -0.90 & 0.1133 & 0.0484 & 0.0489 & 0.0695 \\ 
  17 & 200 & 0 & 1.000 & -0.99 & 0.4477 & 0.0435 & 0.0478 & 0.0438 \\ 
  18 & 200 & 0 & 1.000 & -0.90 & 0.3786 & 0.0501 & 0.0520 & 0.0546 \\ 
  19 & 200 & -1 & 0.995 & -0.99 & 0.3582 & 0.0449 & 0.0483 & 0.0607 \\ 
  20 & 200 & -1 & 0.995 & -0.90 & 0.3127 & 0.0542 & 0.0468 & 0.0615 \\ 
  21 & 200 & -10 & 0.950 & -0.99 & 0.1490 & 0.0401 & 0.0497 & 0.0666 \\ 
  22 & 200 & -10 & 0.950 & -0.90 & 0.1352 & 0.0486 & 0.0502 & 0.0634 \\ 
  23 & 200 & -15 & 0.925 & -0.99 & 0.1276 & 0.0369 & 0.0487 & 0.0786 \\ 
  24 & 200 & -15 & 0.925 & -0.90 & 0.1234 & 0.0482 & 0.0491 & 0.0670 \\ 
\item This Table displays the finite-sample rejection rates of the true null for right-tailed and two-tailed Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively. 10,000 Monte Carlo simulations are performed.
\subsection{Simulation with weakly persistent regressors and Gaussian innovations}
\label{Simulation with weakly persistent regressors and Gaussian innovations}
As argued by Phillips (2014), the Q-test as derived in section (3) is asymptotically invalid when the largest autoregressive root of the regressor is not local to unity. In the following I will demonstrate the finite sample behavior as $\rho$ diverges from unity. Again 10,000 Monte Carlo simulations are run with Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of Campbell and Yogo (2005). Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood the Bonferroni Q-test significantly over-rejects the true null of no predictability. 
\begin{table}[h!]
\caption{Finite-sample rejection rates (non local to unity autoregressive root) }
\label{tab:non-local}
\begin{tabular}{rrrrrrrrr}
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test & Bonf. Q-test (two-sided) \\ 
1 & 50 & 0 & 1.000 & -0.95 & 0.4147 & 0.0946 & 0.0480 & 0.0957 \\ 
  2 & 50 & 0 & 1.000 & -0.75 & 0.2810 & 0.0838 & 0.0475 & 0.0870 \\ 
  3 & 50 & 0 & 1.000 & -0.50 & 0.1758 & 0.0846 & 0.0536 & 0.0940 \\ 
  4 & 50 & -5 & 0.902 & -0.95 & 0.1887 & 0.0896 & 0.0499 & 0.0980 \\ 
  5 & 50 & -5 & 0.902 & -0.75 & 0.1487 & 0.0830 & 0.0522 & 0.0891 \\ 
  6 & 50 & -5 & 0.902 & -0.50 & 0.1081 & 0.0701 & 0.0512 & 0.0811 \\ 
  7 & 50 & -10 & 0.804 & -0.95 & 0.1325 & 0.0894 & 0.0543 & 0.1018 \\ 
  8 & 50 & -10 & 0.804 & -0.75 & 0.1126 & 0.0789 & 0.0462 & 0.0867 \\ 
  9 & 50 & -10 & 0.804 & -0.50 & 0.0887 & 0.0689 & 0.0510 & 0.0820 \\ 
  10 & 50 & -20 & 0.608 & -0.95 & 0.0987 & 0.1266 & 0.0506 & 0.1469 \\ 
  11 & 50 & -20 & 0.608 & -0.75 & 0.0906 & 0.1087 & 0.0506 & 0.1216 \\ 
  12 & 50 & -20 & 0.608 & -0.50 & 0.0682 & 0.0800 & 0.0443 & 0.0948 \\ 
  13 & 50 & -30 & 0.412 & -0.95 & 0.0811 & 0.1666 & 0.0455 & 0.1961 \\ 
  14 & 50 & -30 & 0.412 & -0.75 & 0.0787 & 0.1272 & 0.0500 & 0.1460 \\ 
  15 & 50 & -30 & 0.412 & -0.50 & 0.0719 & 0.1003 & 0.0523 & 0.1195 \\ 
\item This Table displays the finite-sample rejection rates of the true null for right-tailed and two-tailed Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with non local to unity autoregressive root. 10,000 Monte Carlo simulations are performed.
\subsection{Simulation with CCC-GARCH innovations}
\label{Simulation with CCC-GARCH innovations}

@@

\subsection{Simulation with common GARCH innovations}
\label{Simulation with common GARCH innovations}
In the CCC-GARCH model it has been assumed that there are no volatility transmissions between the returns and the regressor. This assumption seems unrealistic and it reduces the correlation between the residuals as demonstrated by $\hat{\delta}$. There are various multivariate GARCH models suited for incorporating spill-over effects such as the BEKK model of Engle and Kroner (1995). It seems plausible, though, that the variances of both the regressor and the returns share a common stochastic trend which may be imagined as the overall economic uncertainty. This seems reasonable since it is hard to imagine having high variance in returns without having high variance in valuation ratios and vice versa. Parameter estimates of the univariate GARCH model based on monthly returns from 1926 to 2003 are displayed in Table~\vref{tab:garch_est}. Since $\hat{\alpha}+\hat{\beta}=0.983$ is close to 1, at which point the covariance stationarity condition is violated, concern of conditional heteroskedasticity of real returns leading to invalid inference using the feasible Q-test is justified.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GARCH(1, 1)} 
  \label{tab:garch_est} 
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00002$ & $2.553$ & $0.011$ \\ 
$\alpha$ & $0.107$ & $0.020$ & $5.331$ & $0.000$ \\ 
$\beta$ & $0.876$ & $0.020$ & $44.365$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
